Analysing the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Change wording, correct typo

---
title: "Analysing the 2024 U.S. Presidential Election"
subtitle: "Spotlight on North Carolina's Role as a Battleground State"
author: 
  - David Qi
  - Haobo Ren
  - Xinrui Xie
thanks: "Code and data are available at: https://github.com/HaoboRrrr/USA_Election"
date: today
date-format: long
abstract: "This paper examines the relationship between polling results and economic conditions to forecast the 2024 U.S. presidential election, with results analyzed for both swing states and at a national level. Findings suggest that Republicans have a modest chance (6.6%) of winning, with North Carolina emerging as the pivotal swing state. The study may offer guidance for campaign strategies and market forcasts. While providing insight on changes of swing states in U.S. politics. "
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

We conclude that Donald Trump have $6.6\%$ probability of winning this election. From our prediction, we highlight North Carolina as the most important battleground state. The state has a predicted $14.2\% $probability to be won by Trump, and will give him 16 electoral votes. Along with the votes that we predict he will almost certainly gain, this pushes him one step (9 electoral votes) to victory. This provide power insight to how campaign and fund raising strategies should be targeted on the election day. And provides a forecast on one of the most important influences in economy in the next several months, which will be especially helpful in planning market stragities.

@@

An alternative approach is to use changes in the DJIA to reflect economic fluctuations. However, we choose to use the absolute DJIA values, as inputing missing days for change data is difficult to justify, and the absolute economic status provides essential insights. Our hypothesis is that a strong economy favors the ruling party in elections, as switching parties could risk economic shifts and potentially lower living standards. Here, the absolute economic level serves as an indicator, reflecting the overall standard of living.

>>>>

---
title: "Analysing the 2024 U.S. Presidential Election"
subtitle: "Spotlight on North Carolina's Role as a Battleground State"
author: 
  - David Qi
  - Haobo Ren
  - Xinrui Xie
thanks: "Code and data are available at: https://github.com/HaoboRrrr/USA_Election"
date: today
date-format: long
abstract: "This paper examines the relationship between polling results and economic conditions to forecast the 2024 U.S. presidential election, with results analyzed for both swing states and at a national level. Findings suggest that Republicans have a modest chance (6.6%) of winning, with North Carolina emerging as the pivotal swing state. The study may offer guidance for campaign strategies and market forcasts. While providing understanding on changes of swing states in U.S. politics and how Florida is no longer a swing state."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

We conclude that Donald Trump have $6.6\%$ probability of winning this election. From our prediction, we highlight North Carolina as the most important battleground state. The state has a predicted $14.2\% $probability to be won by Trump, and will give him 16 electoral votes. Along with the votes that we predict he will almost certainly gain, this pushes him one step (9 electoral votes) to victory. This provide powerful guidence to how campaign and fund raising strategies should be targeted on the election day. And provides a forecast on one of the most important influences in economy in the next several months, which will be especially helpful in planning market stragities.

@@

An alternative approach is to use changes in the DJIA to reflect economic fluctuations. However, we choose to use the absolute DJIA values, as inputing missing days for change data is difficult to justify, and the absolute economic status cannot be reflected by the change in one day. Our hypothesis is that a strong economy favors the ruling party in elections, as switching parties could risk economic shifts and potentially lower living standards. Here, the absolute economic level serves as an indicator, reflecting the overall standard of living.
